---
title: "??Qu?? variables son determinantes para que un estudiante llegue a consumir alcohol en d??a de colegio y en el fin de semana (Dalc y Walc)?"
author: "Carlos Castilla, Bryan Franco y Sebastian Velasco"
date: "6 de septiembre de 2017"
output:
  html_document: default
---

```{r echo=FALSE}
library('ggplot2')
library('ggthemes')
theme_set(theme_tufte())
d1<-read.table("student-mat.csv",sep=",",header=TRUE)
d2<-read.table("student-por.csv",sep=",",header=TRUE)
d3 <- rbind(d1, d2)
```

This dataset we selected has 1044 items, with them we take an insight into alcohol consumption on college students.
It contains 29 variables, most of them categorical:  

**school** - student's school (binary: 'GP' - Gabriel Pereira or 'MS' - Mousinho da Silveira)  
**sex** - student's sex (binary: 'F' - female or 'M' - male)  
**age** - student's age (numeric: from 15 to 22)  
**address** - student's home address type (binary: 'U' - urban or 'R' - rural)  
**famsize** - family size (binary: 'LE3' - less or equal to 3 or 'GT3' - greater than 3)  
**Pstatus** - parent's cohabitation status (binary: 'T' - living together or 'A' - apart)   
**Medu** - mother's education (numeric: 0 - none, 1 - primary education (4th grade), 2 ??? 5th to 9th grade, 3 ??? secondary education or 4 ??? higher education)  
**Fedu** - father's education (numeric: 0 - none, 1 - primary education (4th grade), 2 ??? 5th to 9th grade, 3 ??? secondary education or 4 ??? higher education)  
**Mjob** - mother's job (nominal: 'teacher', 'health' care related, civil 'services' (e.g. administrative or police), 'at_home' or 'other')  
**Fjob** - father's job (nominal: 'teacher', 'health' care related, civil 'services' (e.g. administrative or police), 'at_home' or 'other')  
**reason** - reason to choose this school (nominal: close to 'home', school 'reputation', 'course' preference or 'other')  
**guardian** - student's guardian (nominal: 'mother', 'father' or 'other')  
**traveltime** - home to school travel time (numeric: 1 - <15 min., 2 - 15 to 30 min., 3 - 30 min. to 1 hour, or 4 - >1 hour)  
**studytime** - weekly study time (numeric: 1 - <2 hours, 2 - 2 to 5 hours, 3 - 5 to 10 hours, or 4 - >10 hours)  
**failures** - number of past class failures (numeric: n if 1<=n<3, else 4)  
**schoolsup** - extra educational support (binary: yes or no)  
**famsup** - family educational support (binary: yes or no)  
**paid** - extra paid classes within the course subject (Math or Portuguese) (binary: yes or no)  
**activities** - extra-curricular activities (binary: yes or no)  
**nursery** - attended nursery school (binary: yes or no)  
**higher** - wants to take higher education (binary: yes or no)  
**internet** - Internet access at home (binary: yes or no)  
**romantic** - with a romantic relationship (binary: yes or no)  
**famrel** - quality of family relationships (numeric: from 1 - very bad to 5 - excellent)  
**freetime** - free time after school (numeric: from 1 - very low to 5 - very high)  
**goout** - going out with friends (numeric: from 1 - very low to 5 - very high)  
**Dalc** - workday alcohol consumption (numeric: from 1 - very low to 5 - very high)  
**Walc** - weekend alcohol consumption (numeric: from 1 - very low to 5 - very high)  
**health** - current health status (numeric: from 1 - very bad to 5 - very good)  
**absences** - number of school absences (numeric: from 0 to 93)  

```{r echo=FALSE}
summary(d3)
```

###Scattered plot in which we relate age and number of week days the person drinks and it has been discriminated by sex
```{r}
ggplot(d3, aes(x=age, y=Dalc, color=sex, alpha = 1/10)) + 
  geom_point() +
  scale_colour_hue(l=70) + 
  geom_jitter()
```

###histogram with family relations on x axis with MEAN

```{r}
ggplot(d3, aes(x=famrel)) +
  geom_histogram(binwidth=.5, colour="black", fill="white") +
  geom_vline(aes(xintercept=mean(famrel, na.rm=T)),   # Ignore NA values for mean
             color="red", linetype="dashed", size=1)
```

###histogram with health on x axis with MEAN
```{r}
ggplot(d3, aes(x=health)) +
  geom_histogram(binwidth=.5, colour="black", fill="white") +
  geom_vline(aes(xintercept=mean(health, na.rm=T)),   # Ignore NA values for mean
             color="red", linetype="dashed", size=1)
```
###Dalc vs health colored by sex
```{r}
ggplot(d3, aes(x=Dalc, y=health, color=sex, alpha = 1/10)) + 
  geom_point() +
  scale_colour_hue(l=70) + 
  geom_jitter()
```

###Histogram on a categorical variable for regular day alcohol and fam support
```{r}
ggplot(d3, aes(Dalc, fill = famsup))+ 
  geom_bar()
```

###Histogram on a categorical variable for regular day alcohol and guardian
```{r}
ggplot(d3, aes(Dalc, fill = guardian))+ 
  geom_bar()
```